Continuous risk-based predictive approaches to treatment effect heterogeneity: A simulation study

### 2021-06-30 submission/manuscript.rmd

Another approach would be to assume *constant relative treatment effect* (OR) is
constant. In that case, absolute benefit is estimated from
$\hat{\tau}(\bm{x}) = \text{expit}(PI +\log(\text{OR}))$,
where $\text{expit}(x)=\frac{e^x}{1+e^x}$
and *lp* is the linear predictor of the prediction model.

A different approach fits a logistic regression using treatment, the prognostic
index and their interaction. In this case absolute benefit is estimated from
$\text{expit}(\beta_0+\beta_{PI}PI) - \text{expit}(\beta_0+\beta_{t_x}+(\beta_{PI}+\beta_*)PI)$.
We will refer to this method as the *linear interaction* approach.

>>>>

Another approach would be to assume *constant relative treatment effect* (OR) is
constant. In that case, absolute benefit is estimated from
$\hat{\tau}(\bm{x}) = \text{expit}(PI +\log(\text{OR}))$. This is the method
usually considered when performing risk-based assessment of treatment effect
heterogeneity in RCT data.

A different approach fits a logistic regression using treatment, the prognostic
index and their interaction. In this case absolute benefit is estimated from
$\hat{\tau}(\bm{x})=\text{expit}(\beta_0+\beta_{PI}PI) - \text{expit}(\beta_0+\beta_{t_x}+(\beta_{PI}+\beta_*)PI)$.
We will refer to this method as the *linear interaction* approach.

### 2021-06-30 submission/manuscript.tex

% Pandoc citation processing
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

Another approach would be to assume \emph{constant relative treatment
effect} (OR) is constant. In that case, absolute benefit is estimated
from \(\hat{\tau}(\bm{x}) = \text{expit}(PI +\log(\text{OR}))\), where
\(\text{expit}(x)=\frac{e^x}{1+e^x}\) and \emph{lp} is the linear
predictor of the prediction model.

A different approach fits a logistic regression using treatment, the
prognostic index and their interaction. In this case absolute benefit is
estimated from
\(\text{expit}(\beta_0+\beta_{PI}PI) - \text{expit}(\beta_0+\beta_{t_x}+(\beta_{PI}+\beta_*)PI)\).
We will refer to this method as the \emph{linear interaction} approach.

>>>>

% Pandoc citation processing
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

Another approach would be to assume \emph{constant relative treatment
effect} (OR) is constant. In that case, absolute benefit is estimated
from \(\hat{\tau}(\bm{x}) = \text{expit}(PI +\log(\text{OR}))\). This is
the method usually considered when performing risk-based assessment of
treatment effect heterogeneity in RCT data.

A different approach fits a logistic regression using treatment, the
prognostic index and their interaction. In this case absolute benefit is
estimated from
\(\hat{\tau}(\bm{x})=\text{expit}(\beta_0+\beta_{PI}PI) - \text{expit}(\beta_0+\beta_{t_x}+(\beta_{PI}+\beta_*)PI)\).
We will refer to this method as the \emph{linear interaction} approach.
